Equalizer\\Programming and User Guide

### 2013-02-02 Developer/ProgrammingGuide/paper.tex
Update Developer/ProgrammingGuide/paper.tex

All suitable network interfaces are used to configure the node, that is, the
launch command has to be able to resolve one hostname for starting the render
client processes. Suitable interfaces have to be up and match optional given
values which can be specified by the following command-line parameters:

\begin{description}
\item[--eq-config-flags \textless ethernet\textbar infiniband\textgreater]
  Limit the selection of network interfaces to one of the those types.
\item[--eq-config-prefixes \textless CIDR-prefixes\textgreater] Limit the
  selection of network interfaces that match the given prefix.
\end{description}

@@

\begin{description}
\item[seq] The core namespace for Sequel, the simple interface to the Equalizer
  client library.
\item[eq] The core namespace for the Equalizer client library. The classes and
  their relationship in this namespace closely model the configuration file
  format. The classes in the \textsf{eq} namespace are the main subject of this
  Programming Guide.\fig{fClientUml} provides an overview map of the most
  important classes in the Equalizer namespace, grouped by functionality.
\item[eq::util] The eq::util namespace provides common utility classes, which
  often simplify the usage of OpenGL functions. Most classes in this namespace
  are used by the Equalizer client library, but are usable independently
  from Equalizer for application development.
\item[eq::admin] The eq::admin namespace implements an administrative API to
  change the configurations of a running server. This admin API is not yet
  finalized and will very likely change in the future.
\item[eq::fabric] The eq::fabric namespace is the common data management and
  transport layer between the client library, the server and the administrative
  API. Most Equalizer client classes inherit from base classes in this namespace
  and have all their data access methods in these base classes.
\item[co] Collage is the network library used by Equalizer. It provides basic
  functionality for network communication, such as \textsf{Connection} and
  \textsf{ConnectionSet}, as well as higher-level functionality such as
  \textsf{Node}, \textsf{LocalNode}, \textsf{Object} and
  \textsf{Serializable}. Please refer to \sref{sNetwork} for an introduction
  into the network layer, and to \sref{sNetObject} for distributed objects.
\item[lunchbox] The lunchbox library provides C++ classes to abstract the
  underlying operating system and to implement common helper functionality for
  multi-threaded applications. Examples are \textsf{lunchbox::Clock} providing a
  high-resolution timer, or \textsf{lunchbox::MTQueue} providing a thread-safe,
  blocking FIFO. Classes in this namespace are fully documented in the API
  documentation on the Equalizer website, and are not subject of this
  Programming Guide.
\item[hwloc, boost, vmmlib, hwsd] External libraries providing manual and
  automatic thread affinity, serialization and the foundation for RSP multicast,
  vector and matrix mathematics as well as local and remote hardware (GPU,
  network interfaces) discovery, respectively. The hwloc and hwsd libraries are
  used only internally and not exposed through the API.
\item[eq::server] The server namespace, implementing the functionality of the
  Equalizer server, which is an internal namespace not to be used by application
  developers. The \textsf{eq::admin} namespace enables run-time administration
  of Equalizer servers. The server does not yet expose a stable
  API.
\end{description}

>>>>

All suitable network interfaces are used to configure the nodes, that is, the
launch command has to be able to resolve one hostname for starting the render
client processes. Suitable interfaces have to be up and match optional given
values which can be specified by the following command-line parameters:

\begin{description}
\item[--eq-config-flags \textless ethernet\textbar infiniband\textgreater]
  Limit the selection of network interfaces to one of those types.
\item[--eq-config-prefixes \textless CIDR-prefixes\textgreater] Limit the
  selection of network interfaces that match the given prefix.
\end{description}

@@

\begin{description}
\item[seq] The core namespace for Sequel, the simple interface to the Equalizer
  client library.
\item[eq] The core namespace for the Equalizer client library. The classes and
  their relationship in this namespace closely model the configuration file
  format. The classes in the \textsf{eq} namespace are the main subject of this
  Programming Guide.\fig{fClientUml} provides an overview map of the most
  important classes in the Equalizer namespace, grouped by functionality.
\item[eq::util] The eq::util namespace provides common utility classes, which
  often simplify the usage of OpenGL functions. Most classes in this namespace
  are used by the Equalizer client library, but are usable independently
  from Equalizer for application development.
\item[eq::admin] The eq::admin namespace implements an administrative API to
  change the configurations of a running server. This admin API is not yet
  finalized and will very likely change in the future.
\item[eq::fabric] The eq::fabric namespace is the common data management and
  transport layer between the client library, the server and the administrative
  API. Most Equalizer client classes inherit from base classes in this namespace
  and have all their data access methods in these base classes.
\item[co] Collage is the network library used by Equalizer. It provides basic
  functionality for network communication, such as \textsf{Connection} and
  \textsf{ConnectionSet}, as well as higher-level functionality such as
  \textsf{Node}, \textsf{LocalNode}, \textsf{Object} and
  \textsf{Serializable}. Please refer to \sref{sNetwork} for an introduction
  into the network layer, and to \sref{sNetObject} for distributed objects.
\item[lunchbox] The lunchbox library provides C++ classes to abstract the
  underlying operating system and to implement common helper functionality for
  multi-threaded applications. Examples are \textsf{lunchbox::Clock} providing a
  high-resolution timer, or \textsf{lunchbox::MTQueue} providing a thread-safe,
  blocking FIFO. Classes in this namespace are fully documented in the API
  documentation on the Equalizer website, and are not subject of this
  Programming Guide.
\item[hwloc, boost, vmmlib, hwsd] External libraries providing manual and
  automatic thread affinity, serialization and the foundation for RSP multicast,
  vector and matrix mathematics as well as local and remote hardware (GPU,
  network interfaces) discovery, respectively. The hwloc and hwsd libraries are
  used only internally and are not exposed through the API.
\item[eq::server] The server namespace, implementing the functionality of the
  Equalizer server, which is an internal namespace not to be used by application
  developers. The \textsf{eq::admin} namespace enables run-time administration
  of Equalizer servers. The server does not yet expose a stable
  API.
\end{description}
